---
title: "Figure from - Mapping and prioritizing a regional climate corridor network in the Amazon basin"
author: "Christopher Beirne and Ian McCullough"
format: html
editor: visual
project:
  type: website
  output-dir: docs
---

## Interactive Figures

The following figures are interactive versions of those included in the New Venture Fund project - *Mapping and prioritizing a regional climate corridor network in the Amazon basin*.

It is important to note that the are not exact replicates, but all of the information included in them is the same. 

## Figure 1

Summary figures of the study region.

```{r, echo=F}
library(leaflet)
library(sf)

# Read in the georegions

prov <- st_read("data/regions/Provinces_with_conductance_stats.shp")
prov <- st_transform(prov,4326)


leaflet() %>%  
  addProviderTiles(
    providers$Esri.WorldImagery,
    options = providerTileOptions(opacity = 1)) %>% 
    addPolygons(data = prov, fill=T, color = "black",      weight=3,opacity=1,stroke=T)
  

```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
